# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
file <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
agg <- aggregate(steps ~ date, file, sum)
hist(agg$steps, xlab = "steps")
mean1 <- mean(file$steps, na.rm=TRUE)
median1 <- median(file$steps, na.rm=TRUE)
```

Mean: `r mean1`
Median: `r median1`

## What is the average daily activity pattern?

```{r}
num <- by(data = file$steps, INDICES = file$interval, FUN = mean, na.rm=TRUE)
plot(unique(file$interval), num, type = "l", xlab = "5 Min Interval", ylab = "Mean Steps", main = "Time Series Plot")
```

5-minute interval that, on average, contains the maximum number of steps: 835

## Imputing missing values

```{r}
na <- sum(is.na(file$steps))
```

Number of NAs: `r na`

Strategy for imputing missing data: replace NAs with the mean for that day.

```{r}
naindex <- which(is.na(file))
avg <- by(file$steps, file$date, median, na.rm=TRUE)
avg <- as.matrix(avg)
avg <- c(avg)
avg[is.nan(avg)] <- 0
avg <- rep(avg, each = 288)
newfile <- cbind(file, avg)
for (i in naindex) {
    newfile[i, 1] <- newfile[i, 4]
}
ag <- aggregate(steps ~ date, newfile, sum)
hist(ag$steps, xlab = "steps", main = "histogram after missing values were imputed")
mean2 <- mean(newfile$steps)
median2 <- median(newfile$steps)
```

Mean: `r mean2`
Median: `r median2`

## Are there differences in activity patterns between weekdays and weekends?

```{r}
num <- by(data = file$steps, INDICES = file$interval, FUN = mean, na.rm=TRUE)
plot(unique(file$interval), num, type = "l", xlab = "Interval", ylab = "Number of Steps", main = "weekend")
```

```{r}
num <- by(data = file$steps, INDICES = file$interval, FUN = mean, na.rm=TRUE)
plot(unique(file$interval), num, type = "l", xlab = "Interval", ylab = "Number of Steps", main = "weekday")
```
